### 2025-07-18 paper/quarto_aaai/paper.tex
table adjusted

\input{tables/main.tex}

@@

Test accuracy for CT is virtually identical to the baseline for
\emph{Adult}, \emph{Circ}, \emph{LS}, \emph{Moon}, and \emph{OL}, and
even slightly improved for \emph{Cred}. Exceptions to this general
pattern are \emph{MNIST}, \emph{CH}, and \emph{GMSC}, for which we
observe a reduction in test accuracy of 2, 5, and 15 percentage points
respectively. When looking at robust test accuracies (Acc.\(^*\)) for
these datasets in particular, we find that CT strongly outperforms the
baseline. In fact, we observe that CT improves adversarial robustness on
all datasets.

>>>>

\small
\centering
\input{tables/main.tex}

@@

Test accuracies on adversarially perturbed data are shown in
Figure~\ref{fig-acc}. The perturbations size,
\(\varepsilon \in [0,0.1]\), increases along the horizontal axis and
includes zero, corresponding to standard test accuracy for non-perturbed
data. We observe that for all synthetic datasets, predictive performance
of CT is virtually identical to the baseline and unaffected by
adversarial perturbations. For all real-world datasets, we find that CT
substantially improves robustness: while in some cases baseline
accuracies drop to essentially zero for large enough perturbation sizes,
accuracies for CT are remarkably robust to gradient-based adversarial
attacks.

### 2025-07-18 paper/sections/experiments.qmd
table adjusted

```{=latex}
\input{tables/main.tex}
```

@@

Test accuracy for CT is virtually identical to the baseline for *Adult*, *Circ*, *LS*, *Moon*, and *OL*, and even slightly improved for *Cred*. Exceptions to this general pattern are *MNIST*, *CH*, and *GMSC*, for which we observe a reduction in test accuracy of 2, 5, and 15 percentage points respectively. When looking at robust test accuracies (Acc.$^*$) for these datasets in particular, we find that CT strongly outperforms the baseline. In fact, we observe that CT improves adversarial robustness on all datasets.

>>>>

```{=latex}
\begin{table}[h]
\small
\centering
\input{tables/main.tex}
\end{table}
```

@@

Test accuracies on adversarially perturbed data are shown in @fig-acc. The perturbations size, $\varepsilon \in [0,0.1]$, increases along the horizontal axis and includes zero, corresponding to standard test accuracy for non-perturbed data. We observe that for all synthetic datasets, predictive performance of CT is virtually identical to the baseline and unaffected by adversarial perturbations. For all real-world datasets, we find that CT substantially improves robustness: while in some cases baseline accuracies drop to essentially zero for large enough perturbation sizes, accuracies for CT are remarkably robust to gradient-based adversarial attacks.

### 2025-07-18 paper/sections/other/main_results.qmd
table adjusted

>>>>

df = Serialization.deserialize("paper/experiments/output/final_table.jls")
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
for fname in ["paper/quarto_aaai/tables/main.tex","paper/preprint/tables/main.tex"]
    tabulate_results(
        inputs; 
        table_type=:tabular, 
        save_name=fname, 
        wrap_table=false, 
    )
end
```

### Robust Performance Plots

```{julia}
plt = CTExperiments.plot_performance(res_dir, eps=range(0.0, 0.1, length=10) |> collect, adversarial=true, byvars=["objective", "eps"], drop_synthetic=false)
plt_out = draw(plt, figure=(size=(1000, 150),), axis=(yticks=[0.0,0.5,1.0], limits=(nothing, (0,1)), xticklabelsvisible=false, xticksvisible=false))
save("paper/figures/acc.png", plt_out; px_per_unit=3)
```
